
\newpage
\phantomsection \addcontentsline{toc}{section}{ABSTRACT}

\section*{ABSTRACT}

This report represents the project report on a project entitled "Interactive Voice Response System with Speech Recognition" as a part of the curriculum for the final year project of B.E. in Computer Engineering. The report discusses various methods and implementation techniques to build the system of IVR system with speech recognition and presents the results of the system being implemented. \\
The report represents project work of developing an Interactive Voice Response (IVR) system with the capability of Speech Recognition. It is a system where the user can interact with his/her voice and on the basis of the user's voice input the system performs particular action as a response to the voice command. It is an approach to make use of the voice of the user to recognize the given command instead of using keyboard or other form of input. The project is helpful for various large organizations where there are many call queries or for telecommunications companies or other business ventures where user queries through their voice online or via cellular connections. The system provides an application environment whereby users are prompted to input specific voice commands and the given voice input is being processed for further task accomplishment as per the request.\\
Making use of speech as a input signal significantly increases user experience. Unlike traditional touch-tone or key-press based IVR sytem the system being developed is capable to take a real time voice input from a user. Speech recognition applications are becoming more and more useful nowadays. With growth in the needs for embedded computing and the demand for emerging embedded platforms, it is required that the speech recognition systems (SRS) are available on them too. This project is a simple approach to developing a system where the speech recognition is embedded within another system to automate task using speech as input command. 
