

\section{LIMITATIONS AND FURTHER WORKS}
Speech Recognition has been a very interesting field in research and technology.Many technical teams around the globe are working together to get the satisfactory result.Several researches are ongoing in this field and due to advancement in technology and efficient new models it has made possible to make further enhancement in this field to get more accurate results.Like many other projects our project has also got limitations and the enhancements that can be made in future.

\subsection{Limitations}
Some of the particular field of limitations  are:
\begin{enumerate}
	\item \textbf{Narrow Recognition Domain: }
	Currently the IVR system with speech recognition system works on very narrow domain. Because of time limitation and difficulty in collecting the data samples at present we are focused on using only Nepali numbers from zero to nine in the system.The accuracy level of recognition is dependent on available number of training samples but due to unavailability of training data only fewer data are being trained and recognized.
	\item \textbf{Offline operation: }
	Another limitation of the current system is that it is 
	designed only for the offline operation i.e. available only on desktop environment but not on the web.
	\item \textbf{Narrow application domain: }
	Our present system is focused only in implementation speech recognition on automating a simple task in desktop environment.
	
	
\end{enumerate}

\subsection{Future Enhancements}
The potential enhancements that can be made to the system are discussed below:
\begin{enumerate}
	\item By increasing the training data samples using effective data collection mechanism the domain of recognition can be increased.
	\item The system may be enhanced to make work for online mode by integrating it in web applications.
	\item The system can be enhanced to apply on the real time applications using telephone. For this further research on particular domain is necessary.
\end{enumerate}




